### 2023-04-18 my_paper/tables/tab05-regression.tex
edits

\caption{Effect of Having Hispanic Last Name \label{tab:lastnamereg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcc}
\toprule
  & \specialcell{(1) \\ Log annual earnings} & \specialcell{(2) \\  Log annual earnings}\\
\midrule
$HW_{i}$ & \num{-0.05}** & \num{-0.02}\\
 & (\num{0.02}) & (\num{0.02})\\
\midrule
State FE & X & X\\
Year FE & X & X\\
\textit{Controlling for:} &  & \\
Hours Worked & X & X\\
Age & X & X\\
Education &  & X\\
Observations & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\item[5] \footnotesize{Standard errors are clustered on the state level.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Effect of Having Hispanic Last Name \label{tab:lastnamereg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings}\\
\midrule
$HW_{i}$ & \num{-0.06}** & \num{-0.07}** & \num{-0.05}** & \num{-0.02}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{10.40}*** & \num{9.49}*** &  & \\
 & (\num{0.04}) & (\num{0.07}) &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
Hours Worked &  & X & X & X\\
State FE &  &  & X & X\\
Year FE &  &  & X & X\\
Age FE &  &  & X & X\\
Education FE &  &  &  & X\\
Observations & \num{2423} & \num{2423} & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2023-04-18 output/tables/tab06-regression.tex
edits

\caption{Effect of Having Hispanic Last Name \label{tab:identreg}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings}\\
\midrule
$HW_{i} \times Hispanic_{i}$ & \num{-0.01} & \num{0.04} & \num{-0.02} & \num{-0.02}\\
 & (\num{0.09}) & (\num{0.09}) & (\num{0.08}) & (\num{0.07})\\
$Hispanic_{i}$ & \num{-0.16}** & \num{-0.15}** & \num{-0.11}** & \num{-0.06}\\
 & (\num{0.08}) & (\num{0.07}) & (\num{0.05}) & (\num{0.05})\\
$HW_{i}$ & \num{-0.05} & \num{-0.09} & \num{-0.03} & \num{0.00}\\
 & (\num{0.09}) & (\num{0.08}) & (\num{0.08}) & (\num{0.06})\\
Constant & \num{10.54}*** & \num{9.63}*** &  & \\
 & (\num{0.08}) & (\num{0.11}) &  & \\
\midrule
$HW_{i} \times Hispanic_{i} + Hispanic_{i}$ & -0.17** & -0.11 & -0.13* & -0.08\\
 & (0.08) & (0.07) & (0.07) & (0.06)\\
\midrule
State FE &  &  & X & X\\
Year FE &  &  & X & X\\
\textit{Controlling for:} &  &  &  & \\
Hours Worked &  & X & X & X\\
Age &  &  & X & X\\
Education &  &  &  & X\\
Observations & \num{2423} & \num{2423} & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:iden}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother, and Hispanic is an indicator variable that is equal to one if a person self-identifies as Hispanic.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Effect of Having Hispanic Last Name \label{tab:identreg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings}\\
\midrule
$HW_{i} \times Hispanic_{i}$ & \num{-0.01} & \num{0.04} & \num{-0.02} & \num{-0.02}\\
 & (\num{0.09}) & (\num{0.09}) & (\num{0.08}) & (\num{0.07})\\
$Hispanic_{i}$ & \num{-0.16}** & \num{-0.15}** & \num{-0.11}** & \num{-0.06}\\
 & (\num{0.08}) & (\num{0.07}) & (\num{0.05}) & (\num{0.05})\\
$HW_{i}$ & \num{-0.05} & \num{-0.09} & \num{-0.03} & \num{0.00}\\
 & (\num{0.09}) & (\num{0.08}) & (\num{0.08}) & (\num{0.06})\\
Constant & \num{10.54}*** & \num{9.63}*** &  & \\
 & (\num{0.08}) & (\num{0.11}) &  & \\
\midrule
$HW_{i} \times Hispanic_{i} + Hispanic_{i}$ & -0.17** & -0.11 & -0.13* & -0.08\\
 & (0.08) & (0.07) & (0.07) & (0.06)\\
\midrule
\textit{Controlling for:} &  &  &  & \\
Hours Worked &  & X & X & X\\
State FE &  &  & X & X\\
Year FE &  &  & X & X\\
Age FE &  &  & X & X\\
Education FE &  &  &  & X\\
Observations & \num{2423} & \num{2423} & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] \footnotesize{This table includes the estimation results of equation (\ref{eq:iden}).}
\item[2] \footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother, and Hispanic is an indicator variable that is equal to one if a person self-identifies as Hispanic.}
\item[3] \footnotesize{The sample is restricted to men working full-time full-year and are waged and salaried workers.}
\item[4] \footnotesize{Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.}
\end{tablenotes}
\end{threeparttable}
\end{table}
